Modeling memory and taxis to analyze migrations

### 2021-01-14 code/StrategicVsTactical_PartI_v2.Rmd
Working on indices and streamlining

fr1 <- dnorm(world$X.mid, mean = 80, sd = 10) %>% {./sum(.)/dx}
fr2 <- dnorm(world$X.mid, mean = 20, sd = 10) %>% {./sum(.)/dx}
fixed.Resource <- matrix((fr1 + fr2)/2, byrow = TRUE, 
                         nrow = nrow(world$pop), 
                         ncol = ncol(world$pop))

@@

```{r fixedResource, fig.height = 3, fig.width = 4}
image(Time, X.mid, fixed.Resource, main = "resource", ylab = "x")
```

@@

eval <- FALSE
if(eval){
  ResourceSim <- runManyYears(World, Parameters = parameters, n.years = 3)
  save(ResourceSim, file = "../results/ResourceSim.rda")
} else load("../results/ResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(ResourceSim, tau = tau)
plotYearList(ResourceSim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r exampleResourcePlots, fig.width = 10, fig.height = 6}
source("functions2.R")
Time <- 1:100; X <- 0:100

R1 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 9))
R2 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 5))
R3 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 9))
R4 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 5))

par(mfrow = c(2,2), mar = c(3,3,3,1), mgp = c(2,.25,0), las = 1, tck = 0.01)
image(Time,X,R1, main = "Broad, long peak"); contour(Time,X,R1, add = TRUE)
image(Time,X,R2, main = "Narrow, long peak"); contour(Time,X,R2, add = TRUE)
image(Time,X,R3, main = "Broad, short peak"); contour(Time,X,R3, add = TRUE)
image(Time,X,R4, main = "Narrow, short peak"); contour(Time,X,R4, add = TRUE)
```

@@

In these pulsed resources, we might assume that a *combination* of memory and tactic responses would yield more optimal behavion, and might observe some shift in the migratory strategy.

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(pop.Year1, Time, Resource = R1, Parameters = parameters, n.years = 6)

>>>>

fr1 <- dnorm(world$X.mid, mean = 80, sd = 10) %>% {./sum(.)/world$dx}
fr2 <- dnorm(world$X.mid, mean = 20, sd = 10) %>% {./sum(.)/world$dx}
fixed.Resource <- matrix((fr1 + fr2)/2, byrow = TRUE, 
                         nrow = nrow(world$pop), 
                         ncol = ncol(world$pop))

@@

```{r fixedResource, fig.height = 3, fig.width = 4}
with(world, 
  image(X.mid, 1:tau, resource, main = "resource", ylab = "x")
)
```

@@

eval <- FALSE
if(eval){
  FixedResourceSim <- runManyYears(world, Parameters = parameters, n.years = 3)
  save(FixedResourceSim, file = "../results/FixedResourceSim.rda")
} else load("../results/FixedResourceSim.rda")

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(FixedResourceSim, tau = tau)
plotYearList(FixedResourceSim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

@@

```{r exampleResourcePlots, fig.width = 10, fig.height = 6}
source("functions2.R")

world.R1 <- world %>% 
  list_modify(resource = getPulsedResource(1:world$tau, world$X.mid, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 9)))

R2 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 9, x.peak = 80, x.sd = 5))
R3 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 9))
R4 <- getPulsedResource(Time, X, c(t.peak = 25, t.sd = 5, x.peak = 80, x.sd = 5))

par(mfrow = c(2,2), mar = c(3,3,3,1), mgp = c(2,.25,0), las = 1, tck = 0.01)
with(world.R1, {     
  image(1:tau,X.mid,resource, main = "Broad, long peak")
  contour(1:tau,X.mid,resource, add = TRUE)
  })

image(Time,X,R2, main = "Narrow, long peak"); contour(Time,X,R2, add = TRUE)
image(Time,X,R3, main = "Broad, short peak"); contour(Time,X,R3, add = TRUE)
image(Time,X,R4, main = "Narrow, short peak"); contour(Time,X,R4, add = TRUE)
```

@@

In these pulsed resources, we might assume that a *combination* of memory and tactic responses would yield more optimal behavior, and might observe some shift in the migratory strategy.

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(world.R1, Parameters = parameters, n.years = 6)

par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Memory_PulsedResource_Sim, tau = tau)
plotYearList(Memory_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```
